Truthfulness Verification System

### 2011-05-04 trunk/proposal/paper.tex
strcutred the report

%\begin{algorithm}
%\small
%\caption{Ranking Algorithm 1}
%\label{alg:AssignScore1} 
%\begin{algorithmic}
%\STATE \textbf{Description}: Given the alternate units generated by the current T-verifier system, rank the units in descending order of truthfulness using Wikipedia
%\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each line in this file is a tuple containing the sentence id, the alternate units generated and the topic unit.
%\STATE \textbf{Output}: Ranked alter\_units 
%\FOR {each sentence $s_{i}$}
%	\STATE $tu_{i}$ = topic unit string
%	\STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)
%		
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR	
%	%\FOR{every wiki\_article $w_{p}$ in $list_wiki_articles_au_{s_{i}}$ }
%	%	$bow_w_{p}$ = generate\_bag\_of\_words($w_{p}$)	
%	%	\FOR {every wiki\_article $w_{j}$ in $list_wiki_articles_tu_{j}$  }	
%	%	\ENDFOR
%	%\ENDFOR
%\ENDFOR
%
%
%\end{algorithmic}
%\end{algorithm}
%

\begin{algorithm}
\small
\caption{Ranking Algorithm 1}
\label{alg:AssignScore1}
\begin{algorithmic}
\STATE \textbf{Description}: Given the alternate units generated by
the current T-verifier system, rank the units in descending order of
truthfulness using Wikipedia
\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each
line in this file is a tuple containing the sentence id, the alternate
units generated and the topic unit.
\STATE \textbf{Output}: Ranked alter\_units
\FOR {each sentence $s_{i}$}
       \STATE $tu_{s_{i}}$ = topic unit string
       \STATE $s_{i}.au\_list$ = alternate units generated by T-verifier
       \STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)

@@

\begin{algorithm}
\small
\caption{Find wiki articles}
\label{alg:findwikiarticles}
\begin{algorithmic}
\STATE \textbf{Description}: Given a string of words determine phrases
that may be titles of wikipedia articles
\STATE \textbf{Input}: a string of words $s$
\STATE $l$ = length($s$)
\STATE $result$ = $\phi$
\FOR{$i$ in 1 to $l$}
       \FOR{$j$ in $i$ to $l$}
               \STATE $sub\_string_{ij}$ += $s_i$ + $blank$
       \ENDFOR
       \IF{ $sub\_string_{ij}$ consits only stopwords}
               \STATE discard and continue to next interation
       \ELSE
               \STATE search wikipedia with $sub_string_{ij}$
               \STATE $result_{sub\_string_{ij}}$ = (displaytitle, url, categories,
redirects) for $sub\_string_{ij}$
       \ENDIF
\ENDFOR
\RETURN result
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\small
\caption{Disambiguate articles}
\label{alg:disambiguate}
\begin{algorithmic}
\STATE \textbf{Description}: Given a disambiguation page returns the
wikipedia article that is most relevant to setence being processed
\STATE \textbf{Input}: disambiguation page $p$,$tu_{s_{i}}$
\STATE extract all outlinks urls from the body of the page
\STATE form a dictionary $d$ using disambiguation element ($de$) and
the disambiguation description ($dd$) appearing adjacent to the $de$
\FOR {every $de$ in $d$}
       \STATE $de.ddscore$ = count content word overlap between $dd$ and
($tu_{s_{i}}$ - words in  $de$)
\ENDFOR
\STATE form a dictionary $l$ using disambiguation element ($de$) and
the lead section ($ls$) appearing as the first paragraph of the
article in $de$
\FOR {every $de$ in $l$}
       \STATE $de.lsscore$ = count content word overlap between $ls$ and
($tu_{s_{i}}$ - words in  $de$)
\ENDFOR
\STATE form a dictionary $c$ using disambiguation element ($de$) and
the category list ($cl$) appearing attached with the article on $de$
\FOR {every $de$ in $c$}
       \FOR {every category in $cl$}
               \STATE $de.clscore$ = count content word overlap between $cl$ and
($tu_{s_{i}}$ - words in  $de$)
       \ENDFOR
\ENDFOR
\STATE Reverse sort the $de$s in each method using the scores
\STATE Use Bordas ranking or weighted Bordas to merge the ranks
\RETURN top ranked $de$
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\small
\caption{Ranking Algorithm 2}
\label{alg:AssignScore} 
\begin{algorithmic}
\STATE Search google with topic unit
\STATE take first Wikipedia page from google search result
\STATE Extract all sentences from the Wikipedia page
\FOR{each alternate unit}
	\FOR{each sentence from Wikipedia page}
		\IF{alternate unit is found in the sentence}
			\IF{some content word found in the sentence}
				\STATE return true
			\ELSE
				\STATE return false	
			\ENDIF
		\ENDIF
	\ENDFOR
\ENDFOR		
\STATE assign same score to all true matches

@@

\paragraph{Examples}
Examples of the algorithm described above is discussed below. The algorithm 2 produce perfect result for three of the five sentences. But it struggles with the remaining two sentences. However, the algorithm 2 primarily augment the algorithm 1 and add strength to the results from algorithm 1. Hence they work better together and produce overall better output.

\paragraph{Tom Hanks was the lead actress  int move 'Sleepless in Seattle'}
The alternative units for this sentence are "Tom Hanks", "Meg Ryan", "Hanks Meg", "Nora", and "Sam". Here the sentence containing "Tom Hanks" contain the word actor but not actress. So the algorithm classify it as false. But the sentence containing "Meg Ryan" has the word actress and hence classify it as true. For other alternative units, we don't even get any sentences containing the alternative unit. So the algorithm produce an unambiguous single true statement for this sentence.

\paragraph{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.

\paragraph{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.

\paragraph{English is the Primary Language of the Philippines}
The alternative units for this sentence are "English", "Filipino", "Spanish", "Education", and "History". Our current algorithm struggle with this sentence because of occurrence of content words and alternative units in the same sentence for all the alternative units. So it classify all of them as true and assign same weight to all of them. However, as our algorithm 1 can rank the alternative units in correct order, merged rank from algorithm 1 and algorithm 2 is still correct and produce overall correct result.

\paragraph{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.

\subsection{Rank merging}
This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.

@@

\subsection{Truthfulness verification }
\subsubsection {Building queries from the data supplied by the user}

\subsection{Examples of Truthfulness Verification}

@@

\section{Wikipedia API}

@@

\subsection{With or without the doubt unit}

@@

\subsubsection{Data Description}
The attached file shows the data collected for each sentence from wikipedia. We take the top 10 results returned by searching wikipeida, and calculate the values mentioned above. "S" denotes that $DU$ appears in the snippet, "T", shows that it appears in the Title, and "N" means the $DU$ was not found anywhere. The other values are separated by ';' are title weight,snippet weight,overall result weight.

\subsubsection{Use of answer.com}
We found that answer.com also contains the correct answers to the for the doubt sentences in almost of all the cases. The precise Q\&A format of closely matching the sentences excites us about the possibilities of using the above mentioned strategies for this site. A lot of domain specific sites (like stackexchange.com, quora.com) have become very popular since 2009, which deviate from the traditional forums in the sense that the user generated content is voted, summarised and exposed to a programmatic interface.

>>>>

Pseudo-code for Bag of words ranking is given below. Listing \ref{alg:BagOfWords} produces the ranking for all five alternative units following the procedure described above. It uses Listing \ref{alg:findwikiarticles} to generate k-grams and find relevant Wikipedia pages and Listing \ref{alg:disambiguate} to disambiguate among alternative pages using intersection of words between topic unit and description of disambiguation link for alternative page

%\begin{algorithm}
%\small
%\caption{Bag of Words (Algorithm 1)}
%\label{alg:AssignScore1} 
%\begin{algorithmic}
%\STATE \textbf{Description}: Given the alternate units generated by the current T-verifier system, rank the units in descending order of truthfulness using Wikipedia
%\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each line in this file is a tuple containing the sentence id, the alternate units generated and the topic unit.
%\STATE \textbf{Output}: Ranked alter\_units 
%\FOR {each sentence $s_{i}$}
%	\STATE $tu_{i}$ = topic unit string
%	\STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)
%		
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR	
%	%\FOR{every wiki\_article $w_{p}$ in $list_wiki_articles_au_{s_{i}}$ }
%	%	$bow_w_{p}$ = generate\_bag\_of\_words($w_{p}$)	
%	%	\FOR {every wiki\_article $w_{j}$ in $list_wiki_articles_tu_{j}$  }	
%	%	\ENDFOR
%	%\ENDFOR
%\ENDFOR
%
%
%\end{algorithmic}
%\end{algorithm}
%

\begin{algorithm}
\small
\caption{Bag of Words (Ranking Algorithm 1)}
\label{alg:BagOfWords}
\begin{algorithmic}
\STATE \textbf{Description}: Given the alternate units generated by
the current T-verifier system, rank the units in descending order of
truthfulness using Wikipedia
\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each
line in this file is a tuple containing the sentence id, the alternate
units generated and the topic unit.
\STATE \textbf{Output}: Ranked alter\_units
\FOR {each sentence $s_{i}$}
       \STATE $tu_{s_{i}}$ = topic unit string
       \STATE $s_{i}.au\_list$ = alternate units generated by T-verifier
       \STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)

@@

\begin{algorithm}
\small
\caption{Find wiki articles (called from Bag of Words)}
\label{alg:findwikiarticles}
\begin{algorithmic}
\STATE \textbf{Description}: Given a string of words determine phrases
that may be titles of wikipedia articles
\STATE \textbf{Input}: a string of words $s$
\STATE $l$ = length($s$)
\STATE $result$ = $\phi$
\FOR{$i$ in 1 to $l$}
       \FOR{$j$ in $i$ to $l$}
               \STATE $sub\_string_{ij}$ += $s_i$ + $blank$
       \ENDFOR
       \IF{ $sub\_string_{ij}$ consits only stopwords}
               \STATE discard and continue to next interation
       \ELSE
               \STATE search wikipedia with $sub_string_{ij}$
               \STATE $result_{sub\_string_{ij}}$ = (displaytitle, url, categories,
redirects) for $sub\_string_{ij}$
       \ENDIF
\ENDFOR
\RETURN result
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\small
\caption{Disambiguate articles (called from Bag of Words)}
\label{alg:disambiguate}
\begin{algorithmic}
\STATE \textbf{Description}: Given a disambiguation page returns the
wikipedia article that is most relevant to setence being processed
\STATE \textbf{Input}: disambiguation page $p$,$tu_{s_{i}}$
\STATE extract all outlinks urls from the body of the page
\STATE form a dictionary $d$ using disambiguation element ($de$) and
the disambiguation description ($dd$) appearing adjacent to the $de$
\FOR {every $de$ in $d$}
       \STATE $de.ddscore$ = count content word overlap between $dd$ and
($tu_{s_{i}}$ - words in  $de$)
\ENDFOR
%\STATE form a dictionary $l$ using disambiguation element ($de$) and
%the lead section ($ls$) appearing as the first paragraph of the
%article in $de$
%\FOR {every $de$ in $l$}
%       \STATE $de.lsscore$ = count content word overlap between $ls$ and
%($tu_{s_{i}}$ - words in  $de$)
%\ENDFOR
%\STATE form a dictionary $c$ using disambiguation element ($de$) and
%the category list ($cl$) appearing attached with the article on $de$
%\FOR {every $de$ in $c$}
%       \FOR {every category in $cl$}
%               \STATE $de.clscore$ = count content word overlap between $cl$ and
%($tu_{s_{i}}$ - words in  $de$)
%       \ENDFOR
%\ENDFOR
%\STATE Reverse sort the $de$s in each method using the scores
%\STATE Use Bordas ranking or weighted Bordas to merge the ranks
\RETURN top ranked $de$
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\small
\caption{Sentence Structure (Ranking Algorithm 2)}
\label{alg:SentenceStructure} 
\begin{algorithmic}
\STATE Search google with topic unit
\STATE take first Wikipedia page from google search result
\STATE Extract all sentences from the Wikipedia page
\FOR{each alternate unit}
	\FOR{each sentence from Wikipedia page}
		\IF{alternate unit is found in the sentence}
			%\IF{some content word found in the sentence}
			%	\STATE return true
			%\ELSE
			%	\STATE return false	
			%\ENDIF
			\STATE count [alternate unit]= no of intersection of content words from topic unit and the sentence
		\ENDIF
	\ENDFOR
\ENDFOR		
\STATE rank the alternate units using descending order of count[alternate unit]

@@

\paragraph{Examples}
Detail working of Sentence Structure (Algorithm 2) is described for following sentence is given below:

\emph{Les Paul invented the electric guitar}

For this sentence the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. The top wikipedia page from google search is http://en.wikipedia.org/wiki/Electric\_guitar. So we download this page. Convert it to text from html and split into sentences. Then we match each alternate unit with all the sentences to see if there is any intersection with the alternate unit. We found intersection for the alternate units les paul, gibson les, llyod, and adolph rickenbaker but not for leo. Hence leo get a score of zero and we process other alternative units further. In the next step, we find intersection between content words or topic unit and matched sentences for alternate units found in the previous step. We count no of words that are overlapped and rank alternate units according to this count value. Count of the content word overlap is given below.

3 les paul\\
1 gibson les\\
0 llyod\\
0 leo\\
0 adolph rickenbacker

 It shows that we have 3 content word intersection for les paul, 1 word intersection for gibson les and 0 for all other alternate units. This ranking is the final truth or confidence ranking for all alternate units

%\paragraph{Examples}
%Examples of the algorithm described above is discussed below. The algorithm 2 produce perfect result for three of the five sentences. But it struggles with the remaining two sentences. However, the algorithm 2 primarily augment the algorithm 1 and add strength to the results from algorithm 1. Hence they work better together and produce overall better output.
%
%\paragraph{Tom Hanks was the lead actress  int move 'Sleepless in Seattle'}
%The alternative units for this sentence are "Tom Hanks", "Meg Ryan", "Hanks Meg", "Nora", and "Sam". Here the sentence containing "Tom Hanks" contain the word actor but not actress. So the algorithm classify it as false. But the sentence containing "Meg Ryan" has the word actress and hence classify it as true. For other alternative units, we don't even get any sentences containing the alternative unit. So the algorithm produce an unambiguous single true statement for this sentence.
%
%\paragraph{Les Paul invented the electric guitar}
%The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.
%
%\paragraph{Luna 2 is the first spacecraft on the moon}
%The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.
%
%\paragraph{English is the Primary Language of the Philippines}
%The alternative units for this sentence are "English", "Filipino", "Spanish", "Education", and "History". Our current algorithm struggle with this sentence because of occurrence of content words and alternative units in the same sentence for all the alternative units. So it classify all of them as true and assign same weight to all of them. However, as our algorithm 1 can rank the alternative units in correct order, merged rank from algorithm 1 and algorithm 2 is still correct and produce overall correct result. 
%
%\paragraph{Sullivan is the fastest swimmer in the world}
%The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.
%
%\subsection{Rank merging}
%This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.
%
%

@@

@@

\subsection {Building queries from the data supplied by the user}

\subsection{Wikipedia API}

@@

\subsubsection{With or without the doubt unit}

@@

%\subsubsection{Data Description}
%The attached file shows the data collected for each sentence from wikipedia. We take the top 10 results returned by searching wikipeida, and calculate the values mentioned above. "S" denotes that $DU$ appears in the snippet, "T", shows that it appears in the Title, and "N" means the $DU$ was not found anywhere. The other values are separated by ';' are title weight,snippet weight,overall result weight.
% 
\subsection{Use of answer.com}
We found that answer.com also contains the correct answers to the for the doubt sentences in almost of all the cases. The precise Q\&A format of closely matching the sentences excites us about the possibilities of using the above mentioned strategies for this site. A lot of domain specific sites (like stackexchange.com, quora.com) have become very popular since 2009, which deviate from the traditional forums in the sense that the user generated content is voted, summarised and exposed to a programmatic interface.
